---
title: "Juvenile_Competition"
author: "Angie Coulter"
date: "04/02/2020"
output: github_document
---

## Data Preparation
Load packages needed for data wrangling and plotting.
```{r results='hide', message=F}
library(dplyr)
library(ggplot2)
library(tidyr)
library(cowplot)
library(lme4)
library(lmerTest)
```

Import growth and mortality data. 
```{r}
lw <- read.csv("Juv_Length_Weight.csv", header=T)
mort <- read.csv("Juv_Mort.csv", header=T)
```

Specific Growth Rate
```{r warning=F, message=F, dpi=300}
wtfin <- lw %>%
  filter(Week == 4) %>%
  group_by(Tank,Treatment,Density,Ration)
wtin <- lw %>%
  filter(Week == 0) %>%
  group_by(Tank,Treatment,Density,Ration)

gr <- left_join(wtfin,wtin, by = c("Tank", "FishID", "Density", "Ration","Treatment"))
gr <- gr %>%
  select(-Date.x,-Date.y,-Week.x,-Week.y,-Note.x,-Note.y,-Length.x,-Length.y)
gr$sgr <- ((log(gr$Mass.x)-log(gr$Mass.y))/28)*100

sgr <- gr %>%
  group_by(Tank,Treatment,Density,Ration) %>%
  summarise(sgrm = mean(sgr,na.rm = T),
            sgrsd =sd(sgr, na.rm = T))

p <- ggplot(sgr, aes(x=Density, y=sgrm,color=Ration)) + geom_point()
p <- p + scale_x_continuous(limits = c(1,7), breaks=seq(1,7,2))
p <- p + scale_y_continuous(limits = c(0.5,3), breaks=seq(0.5,3,0.5))
p <- p + geom_smooth(method = "lm")
p <- p + theme_classic()
p <- p + xlab("Density (Fish/Tank)")
p <- p + ylab("Specific Growth Rate (%/day)")
p

lm <- lm(sgr$sgrm ~ sgr$Density * sgr$Ration)
anova(lm)

```

ANCOVA for final mass with ration as covariate
```{r warning=F, message=F, dpi=300}
lw$LnMass <- log(lw$Mass)

tankfin <- lw %>%
  filter(Week == 4, Note != "Stuck in filter") %>%
  group_by(Tank,Treatment,Density,Ration) %>%
  summarise(MeanWt = mean(Mass,na.rm = T),
            SDWt =sd(Mass, na.rm = T),
            MeanLnWt = mean(LnMass,na.rm = T),
            SDLnWt =sd(LnMass, na.rm = T))

p <- ggplot(tankfin, aes(x=Density, y=MeanWt,color=Ration)) + geom_point()
p <- p + scale_x_continuous(limits = c(1,7), breaks=seq(1,7,2))
p <- p + scale_y_continuous(limits = c(2,10), breaks=seq(2,10,2))
p <- p + geom_smooth(method = "lm")
p <- p + theme_classic()
p <- p + xlab("Density (Fish/Tank)")
p <- p + ylab("Mass (Grams)")
p

lm <- lm(tankfin$MeanWt ~ tankfin$Density * tankfin$Ration)
anova(lm)

q <- ggplot(tankfin, aes(x=Density, y=MeanLnWt,color=Ration)) + geom_point()
q <- q + scale_x_continuous(limits = c(1,7), breaks=seq(1,7,2))
q <- q + scale_y_continuous(limits = c(1,2.5), breaks=seq(1,2.5,.5))
q <- q + geom_smooth(method = "lm")
q <- q + theme_classic()
q <- q + xlab("Density (Fish/Tank)")
q <- q + ylab("Ln(Mass) (Grams)")
q

lmln <- lm(tankfin$MeanLnWt ~ tankfin$Density * tankfin$Ration)
anova(lmln)
```

Log-Linear regression for mortality count

Use a poisson distribution because count data is not normal

Use a chi-square test in the ANOVA command for same reason
```{r warning=F, message=F, dpi=300}
morttot <- read.csv("Juv_Mort_Total.csv",header=T)

p <- ggplot(morttot, aes(Density,TotalMort, color=Ration)) + geom_point()
p <- p + scale_x_continuous(limits = c(1,7), breaks=seq(1,7,2))
p <- p + ylab("Count of Mortality")
p <- p + xlab("Density (Fish/Tank)")
p <- p + geom_smooth(method = "lm")
p <- p + theme_classic()
p

y <- glm(TotalMort ~ Density * Ration, family=poisson, data=morttot)
anova(y, test="Chisq")

#Evaluating assumptions of the glm() fit
#A central property of the Poisson distribution is that the variance and mean are equal 
tapply(morttot$TotalMort, morttot$Density, mean)
tapply(morttot$TotalMort, morttot$Density, var)
```

Alive and Dead Mass Comparison
```{r warning=F, message=F, dpi=300}
#Assign lw data to Alive status
#Remove records of dead fish
lw$Status <- "Alive"
al <- lw %>% 
  filter(Note != "Mort")

#Add Dead status
mort$Status <- "Dead"

juv <- bind_rows(al,mort) %>%
  select(-Colour)
juv$Date <- as.Date(juv$Date, "%m-%d-%Y")

#Remove some outliers: dried to floor and trapped in filter
juv <- juv[-c(388,437),] 

ids <- read.csv("Juv_Fish_ID.csv")

juv <- left_join(juv,ids)
juv$Status <- as.factor(juv$Status)

juv$LnMass <- log(juv$Mass)

juvsum <- juv %>%
  group_by(Week,Treatment,Status)%>%
  filter(Week != 0)%>%
  summarise(meanwt = mean(Mass, na.rm = T),
            sdwt = sd(Mass, na.rm = T),
            meanlnwt = mean(LnMass, na.rm = T),
            sdlnwt = sd(LnMass, na.rm = T))

limits <- aes(ymax = juvsum$meanlnwt + juvsum$sdlnwt,
              ymin = juvsum$meanlnwt - juvsum$sdlnwt)

p <- ggplot(juvsum,aes(Treatment,meanlnwt,fill = factor(Status))) + geom_bar(position = position_dodge2(preserve = "single"), stat="identity") + facet_wrap(juvsum$Week) + scale_fill_discrete(name = "Status")
p <- p + geom_errorbar(limits, width = 0.1, position=position_dodge(.9))
#p <- p + geom_errorbar(aes(ymin = mean - sdwt, ymax = mean + sdwt, fill = factor(Living)), width=0.2) 
p <- p + ylab("Ln(Mass) (g)")
p <- p + theme_bw()
p

lme <- lmer(LnMass ~ Density + Ration + Status + Date + (1|Tank) + (1|FishUn), juv)
summary(lme)
anova(lme, type = 3)
ranova(lme)

```


Feb 4th: Tank Conversion Measures
Feeding Efficiency

```{r warning=F, message=F, dpi=300}
#Import tank mass and feed to calculate conversions
conv <- read.csv("Juv_Mass_Feed_Tank.csv", header = T)

#Calculate feed efficiency: out/in
conv$FE <- conv$Mass_Gained/conv$Feed


FE <- conv %>%
  group_by(Treatment) %>%
  summarise(FE_Mean = mean(FE),
            FE_SD =sd(FE))

q <- ggplot(conv, aes(Treatment,FE))
q <- q + geom_boxplot(outlier.colour="black", outlier.shape=16, outlier.size=2, notch=FALSE)
q <- q + ylab("Feed Efficiency")
q <- q + xlab("Treatment")
q <- q + theme_classic()
q <- q + scale_y_continuous(expand = c(0,0), limits = c(0.25,2.25), breaks = seq(0.25,2.25,0.25))
q <- q + ggtitle("Feed Efficiency (Growth/Feed)")
q

p <- ggplot(conv, aes(x=Density, y=FE,color=Ration)) + geom_point()
p <- p + scale_x_continuous(limits = c(1,7), breaks=seq(1,7,2))
p <- p + scale_y_continuous(limits = c(0,2.5), breaks=seq(0,2.5,.5))
p <- p + geom_smooth(method = "lm")
p <- p + theme_classic()
p <- p + xlab("Density (Fish/Tank)")
p <- p + ylab("Feed Efficiency")
p

lm <- lm(conv$FE ~ conv$Density * conv$Ration)
anova(lm)

```


Feed Conversion Rate
```{r warning=F, message=F, dpi=300}
#Calculate food conversion rate: in/out
conv$FCR <- conv$Feed/conv$Mass_Gained

FCR <- conv %>%
  group_by(Treatment) %>%
  summarise(FCR_Mean = mean(FCR),
            FCR_SD =sd(FCR))

p <- ggplot(conv, aes(Treatment,FCR))
p <- p + geom_boxplot(outlier.colour="black", outlier.shape=16, outlier.size=2, notch=FALSE)
p <- p + ylab("Food Conversion Rate")
p <- p + xlab("Treatment")
p <- p + theme_classic()
p <- p + scale_y_continuous(expand = c(0,0), limits = c(0.25,3), breaks = seq(0.25,3,0.25))
p <- p + ggtitle("Food Conversion Rate (Feed/Growth)")
p

p <- ggplot(conv, aes(x=Density, y=FCR,color=Ration)) + geom_point()
p <- p + scale_x_continuous(limits = c(1,7), breaks=seq(1,7,2))
p <- p + scale_y_continuous(limits = c(0,3), breaks=seq(0,3,.5))
p <- p + geom_smooth(method = "lm")
p <- p + theme_classic()
p <- p + xlab("Density (Fish/Tank)")
p <- p + ylab("Feed Conversion Rate")
p

lm <- lm(conv$FCR ~ conv$Density * conv$Ration)
anova(lm)

```

